\ \break Automatikus korpuszépítés tulajdonnév-felismerés céljára

### 2013-01-04 paper/MSZNY2013/mszny_slides.tex
Something.
The corpus description has been moved to the end.

\subsection{Tulajdonnevek címkézése}
\begin{frame}{Tulajdonnevek címkézése}
  \bigskip
  \begin{itemize}
  \vitem Tulajdonnevek felismerése:
    \begin{itemize}
    \vitem Look up linked pages in the entity list
    \vitem References to the current page, if in the list
    \end{itemize}
  \vitem NE tagging: from the DBpedia--CoNLL category mapping
  \vitem Kivételek:
    \begin{itemize}
    \vitem Cikkek, amik nem entitások: nagybetűvel kell kezdődjön a szócikk
    \vitem Jelöletlen entitások: megpróbáljuk őket korábbi tulajdonnevekhez kötni
    \vitem Speciális esetek: tulajdonnév-köznév összetételek, mondatkezdő főnevek, stb.
    \end{itemize}
  \end{itemize}
\end{frame}

@@

%TODO: the "Hungarian Corpus" phrase must appear in the frame title 
\begin{frame}{Differences from English}
  \bigskip
  \begin{itemize}
  \vitem Language processing tools
    \begin{itemize}
    \vitem Inflectional morphology: different set of tools were needed 
    \vitem We developed a flexible framework that enables the plugging of any NLP tool
    % TODO: what kind of linguistic tools are needed: table?
    \end{itemize}
  \vitem Wikipedia size and coverage
    \begin{itemize}
    \vitem Hungarian is medium-size language: \nagytilde 200k articles vs.~\nagytilde 4M English pages
    \vitem Cross-references may point to English pages
    \vitem Templates are in Hungarian: per-language template configuration
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{tabular}{lllllll}
\textbf{token} & \textbf{text/link} & \textbf{WP link} & \textbf{POS} & \textbf{lemma} & \textbf{NE} \\
Neumann & B-link & Neumann János & NOUN & neumann & B-PER & B-PER \\
János & I-link & Neumann János & NOUN & jános & I-PER & I-PER \\
( & text & 0 & PUNCT & ( & O & O \\
1903–1957 & text & 0 & NUM & 1903–1957 & O & O \\
) & text & 0 & PUNCT & ) & O & O \\
matematikai & text & 0 & ADJ & matematikai & O & O \\
szemszögből & text & 0 & NOUN<CAS<ELA>> & szemszög & O & O \\
közelíti & text & 0 & VERB<DEF> & közelít & O & O \\
meg & text & 0 & PREV & meg & O & O \\
a & text & 0 & ART & a & O & O \\
kérdést & text & 0 & NOUN<CAS<ACC>> & kérdés & O & O \\
\end{tabular}

@@

>>>>

\subsection{Tulajdonnevek címkézése}
\begin{frame}{Tulajdonnevek címkézése}
  \bigskip
  \begin{itemize}
  \vitem Tulajdonnevek felismerése szövegben:
    \begin{itemize}
    \vitem Kereszthivatkozások, ha a hivatkozott cikk szerepel az entitáslistában
    \vitem Az aktuális cikk címe, ha szerepel a listában
    \end{itemize}
  \vitem Címkézés: a DBpedia--Szeged leképezés alapján
  \vitem Kivételek:
    \begin{itemize}
    \vitem Cikkek, amik nem entitások: nagybetűvel kell kezdődjön a szócikk
    \vitem Jelöletlen entitások: megpróbáljuk őket korábbi tulajdonnevekhez kötni
    \vitem Speciális esetek: tulajdonnév-köznév összetételek, mondatkezdő főnevek, stb.
    \end{itemize}
  \end{itemize}
\end{frame}

@@

%TODO: the "Hungarian Corpus" phrase must appear in the frame title 
\begin{frame}{Nyelvfüggetlenség}
\end{frame}

\begin{frame}{Differences from English}
  \bigskip
  \begin{itemize}
  \vitem Language processing tools
    \begin{itemize}
    \vitem Inflectional morphology: different set of tools were needed 
    \vitem We developed a flexible framework that enables the plugging of any NLP tool
    % TODO: what kind of linguistic tools are needed: table?
    \end{itemize}
  \vitem Wikipedia size and coverage
    \begin{itemize}
    \vitem Hungarian is medium-size language: \nagytilde 200k articles vs.~\nagytilde 4M English pages
    \vitem Cross-references may point to English pages
    \vitem Templates are in Hungarian: per-language template configuration
    \end{itemize}
  \end{itemize}
\end{frame}

@@

@@

% TODO: nem fér ki minden oszlop
\begin{tabular}{lllllll}
\textbf{token} & \textbf{text/link} & \textbf{WP link} & \textbf{POS} & \textbf{lemma} & \textbf{NE} \\
Neumann & B-link & Neumann János & NOUN & neumann & B-PER & B-PER \\
János & I-link & Neumann János & NOUN & jános & I-PER & I-PER \\
( & text & 0 & PUNCT & ( & O & O \\
1903–1957 & text & 0 & NUM & 1903–1957 & O & O \\
) & text & 0 & PUNCT & ) & O & O \\
matematikai & text & 0 & ADJ & matematikai & O & O \\
szemszögből & text & 0 & NOUN<CAS<ELA{>}> & szemszög & O & O \\
közelíti & text & 0 & VERB<DEF> & közelít & O & O \\
meg & text & 0 & PREV & meg & O & O \\
a & text & 0 & ART & a & O & O \\
kérdést & text & 0 & NOUN<CAS<ACC{>}> & kérdés & O & O \\
\end{tabular}
